formula1

### 2020-06-06 inst/f1points.Rmd
clarification and better idiom

```{r,label=calcpoints}
p <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
dp <- ordertable2points(as.ordertable(F1_table_2017[seq_len(top),]),p)
dp
dp <- dp[order(-dp)]
dp[] <- seq_along(dp)
```
now likelihood

>>>>

```{r,label=calcpoints}
p <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
dp <- ordertable2points(as.ordertable(F1_table_2017[seq_len(top),]),p)
dp
dp <- sort(dp,decreasing=TRUE)
dp[] <- seq_along(dp)
dp
```
now likelihood
